### 2021-06-29 docs/submission/srep/coverletter/letter-tex/covlet.tex
#15 updates title in coverletter

%* A brief explanation of why the work is appropriate for Scientific Reports
Our work is appropriate for Scientific Reports due to its alignment to the principles of open science (e.g., reproducibility, transparency, reusability and open accessibility) in the fields of physical, biological, health and engineering sciences.
Similarly, we choose Scientific Reports as venue where potential interest of readers in above mentioned areas along with raising interested and spark collaborations.

>>>>

%* A brief explanation of why the work is appropriate for Scientific Reports
Our work is appropriate for Scientific Reports due to its alignment to the principles of open science (e.g., reproducibility, transparency, reusability and open accessibility) in the fields of physical, biological, health and engineering sciences.
Similarly, we choose Scientific Reports as venue for publication of multidisciplinary areas where potential interest of readers may be interested and spark collaborations of our work.
